Discovery of Rotational Modulations in the Planetary-mass Companion 2M1207\lowercase{b}: Intermediate Rotation Period and Heterogeneous Clouds in a Low Gravity Atmosphere

### 2015-12-11 summary/letter/letter_vAI.tex
duech

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\bibliographystyle{apj}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mbox{Jup}}$}
\newcommand{\revise}[1]{\textbf{{\color{cyan}{#1}}}}
\renewcommand{\revise}{}
\newcommand{\period}{$10.5^{+1.5}_{-0.8}$}
\newcommand{\Jperiod}{$11.1^{+2.0}_{{-1.2}}$}
\newcommand{\Jamp}{$1.36\pm0.23 \%$}
\newcommand{\Hperiod}{$9.3^{+2.0}_{{-0.8}}$}
\newcommand{\Hamp}{$0.78\pm0.22 \%$}
\begin{document}

@@

\begin{abstract}
  Rotational modulations of brown dwarfs have recently provided
  powerful constraints on the properties of ultra-cool atmospheres,
  including longitudinal and vertical cloud structures and cloud
  evolution. Furthermore, periodic light curves directly probe the
  rotational periods of ultra-cool objects.  We present here, for the
  first time, time-resolved high-precision photometric measurements of
  a planetary-mass companion, 2M1207b.  We observed the binary
  system with HST/WFC3 in two bands and with two spacecraft roll
  angles. Using point spread function-based photometry, we reach a
  nearly photon-noise limited accuracy for both the primary and the
  secondary. While the primary is consistent with a flat light curve,
  the secondary shows modulations that are clearly detected in the
  combined light curve as well as in different subsets of the data.
  The amplitudes are 1.36\% in the F125W and 0.78\% in the F160W
  filters, respectively. We find a consistent period of
\period{} hours and
  similar phases in both bands. The J- and H-band amplitude ratio of
  2M1207b is very similar to a field brown dwarf that has identical
  spectral type but different J-H color.  Importantly, our study also
  measures, for the first time, the rotation period for a directly 
  imaged planetary-mass companion to another star.
\end{abstract}

@@

The observations applied space craft rolls each two orbits to allow
roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
telescope roll angles for orbit 1, 3, and 5, and those for 2, 4, and 6
differed by $25^{\circ}$. At the separation of 2M1207b, this angle
difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
resolution elements in F125W and F160W, respectively.
%In each orbit we took 8 SPARS10 exposure sequence with NSAMP=10,
%alternating between F160W and F125W filters, with 2--3 identical
%exposures in each exposure sequence.
\revise{In each orbit, we took 8 SPARS 10 exposure sequences
  alternating between F125W and F160W filters. Each sequence contained
  2--3 identical exposures that had 10 non-destructive read-outs and total
  exposure time of 88.4 s.} To improve sampling and reduce the risk
that the core of point spread function (PSF) is affected by bad
pixels, we applied a 4-point dither pattern with differential ``X/Y''
offsets of 1.375" in the detector frame, providing optimal
non-integral (half pixel) step of 10.5 and 8.5 pixels in F125W and
F160W, respectively. In total, we obtained 70 and 64 images with 10 in
F125W and F160W, respectively.

@@

 \begin{figure*}
  \centering
  \plotone{systematics}
  \caption{F125W (left) and F160W (right) light curves under different
    variability verification tests. Individual measurements are
    plotted with gray crosses. Photometric measurements of the same exposure
    sequence are binned, and binned photometry are plotted with points
    or squares. Best fitted sinusoids are plotted with solid
    lines. {\em Upper}: binned measurements taken in dithering
    position 1 and 3 (red points) and that taken in 2 and 4 (blue
    squares) are plotted with different symbols. They demonstrate same
    trend of modulation. In upper left panel, the green line a sinusoid
    fitted with all parameters freely varying, and the purple line is
    a sinusoid fitted with the period set the same as that of
    F125W. {\em Middle}: sinusoids fitted without using the
    data taken in Orbit \#1. These curves are almost identical to the
    curves plotted in upper panel. {\em Lower}: photometry measured
    with AFEM-added images and best fitted sinul curves. These
    points and curves are also almost identical to those plotted
    in the upper panel.}
  \label{fig:2}

@@

For both of 2 steps, we used \tinytim{} to calculate 10$\times$
over-sampled model PSFs based on the filters, the spectra (2M1207A:
\cite{Bonnefoy2014}, 2M1207b: \cite{Patience2010}), the telescope's
actual focus, and the telescope jitter.  We used the set of \tinytim{}
parameters provided by \cite{Biretta2014} to improve modeling the cold
mask, diffraction spikes, and the coma. The focus parameters are 
interpolated to the precise time of the observations using the
tabulated values provided by
STScI\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
To align the \tinytim{} PSF to the observed PSF of 2M1207A, we
moved the over-sampled PSF on a coordinate grid (gird size=0.001 pixel)
using cubic interpolation, and searched for the position that minimizes
the rms difference of the observed and the re-binned \tinytim{} PSF over
a region centered on 2M1207A with a 5-pixel-radius aperture centered
on 2M1207b excluded.  Then we introduced another \tinytim{} PSF for
2M1207b and fit the position of 2M1207b and the scales of the
\tinytim{} PSFs of 2M1207A and b simultaneously by minimizing the
residual from both primary and secondary. In the first step, we discovered that the
difference of observed PSFs and model PSFs was very stable for a
specified telescope roll angle and dithering position. Therefore, at the end of the first step,
we derive 8 (2 roll angles $\times$ 4 dithering positions) correction
maps for each filter:
\begin{equation}
  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
\end{equation}
where $\mathrm{PSF_{model}}$ was a combination of two scaled \tinytim{} PSFs
for 2M1207A and b. In the second round, we combined the correction
map linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
and scaled the correction map together with the two PSFs so that the
residual, which is expressed as
\begin{equation}
  \mathrm{residual} = \mathrm{Image} - a\cdot \mathrm{PSF_{A}} - b\cdot
    \mathrm{PSF_{b}}- c\cdot\mathrm{ Corr}
  \end{equation}
  is minimized by least square fitting.
We found that by introducing the correction term,
the reduced $\chi^{2}$ was decreased from $\sim 10$ to
$\sim 1$. Relative photometry was acquired from the scaling
parameters of the \tinytim{} PSFs.

Our final step was to correct for a slight apparent trend between the
position of the targets on the detector and their flux. We attributed
this to a combination of slight changes in the PSF profile due to
pixelation and to the effect of imperfectly corrected pixel-to-pixel
sensitivity variations. We corrected for these apparent
position-dependent flux changes by normalizing each photometric point
by the median of all fluxes measured when the target was at the
same position, i.e. combining data over 6 orbits.  We note that this
correction was small and, as we demonstrate in the next sections,
could not introduce artificial modulations that resemble the long-period
variations that we identified in 2M1207b.

@@

\label{Results}

@@

First, we fitted sinusoids independently to the light curves of two
filters to verify the similarity of the signal in the two bands
(Figure \ref{fig:2}, top panel). Inconsistent periods or light curve
shapes would argue against a genuine signal.  We found that the periods
of the best fit sine waves were similar, \Jperiod{} h for
F125W and \Hperiod{} h for F160W. These periods are consistent
within the uncertainty. Furthermore, these periods are not close to
any timescales over which HST or WFC3 changes, and are
very different from all timescales present in our observations
(dithering timescales, integration times, and orbital timescales).

As a second test, we repeated the analysis neglecting the first
orbit. The motivation behind this test is that, due to spacecraft
thermal settling, the first orbits of HST observations are often
slightly unstable, and are neglected in high-precision studies
\citep[e.g.][]{Mandell2013}. Indeed, in our analysis, 2M1207A is
significantly fainter in the first orbit (Figure \ref{fig:3}) than in
the subsequent ones.  Our analysis based on orbits 2--6 found
essentially identical results to our analysis using the whole 6 orbits, based on
which we conclude that the first less reliable orbit does not affect
our results significantly (Figure \ref{fig:2}, middle panel).

@@

\subsection{Amplitude and Period Measurements}

% We used a MC method to analyze the light curve, and provided amplitudes
% and periods as well as their uncertainties for both filters. We
% generated series of Gaussian distributed random noise with standard deviation
% same as the photon noise, added the noise to the original light curves, and
% fitted sinusoids to the newly combined light curves. We repeated these
% procedures  for 100,000 times and obtain the distributions of period
% and amplitude (Figure \ref{fig:4}).

@@

\revise{To further constrain the amplitudes and periods of the light
  curves, we performed sinusoidal fit using Markov Chain Monte Carlo
  (MCMC) method.  The priors for the amplitudes, the periods and the
  phases of the sine waves were all assumed to be uniform
  distributions. The ranges of the prior distributions were 0 to 5\%
  for the amplitudes, 2 to 40 hours for the periods, and 0 to $2\pi$
  for the phases. The results of the MCMC fit are shown in Figure
  \ref{fig:4}. The posterior distributions of the periods and amplitudes
  are very well constrained for both two filters so that we are able
  to measure the amplitudes and periods as well as their
  uncertainties. For F125W, the amplitude and period are \Jamp{} and
  \Jperiod{}, respectively, and for F160W, they are \Hamp{} and
  \Hperiod{}, respectively. We also repeated the fitting excluding data from the
  first orbit in order to quantitatively assess the influence of these
  less stable data points. Even in the case of limiting
  our data to Orbits 2-6, the posterior probability distribution peaks
  at  periods and amplitudes very similar to those found for the entire dataset,
  demonstrating that a periodic solution is preferred with or without
  the first orbit data. Nevertheless, unsurprisingly, when shortening
  the baseline by considering only Orbits 2-6 results in a long-period
  tail in the probability distribution.}

@@

\section{Result}

We present the first high-contrast, high-cadence, and high-precision
photometry of a directly imaged planet or planetary-mass
companion around another star. Our observations reveal a modulation in the light curve of
the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
of modulations in directly imaged planetary-mass objects. The best
fit periods for F125W and F160W are $11.1_{-1.2}^{+2.0}$ and $9.3_{-0.8}^{+2.0}$ hours,
respectively. We also fitted the two band light curves together forcing the
periods of two sinusoids to be the same, and obtained a period
of \period{} hours.

We obtained high signal to noise photometry for both 2M1207A
and B (Figure \ref{fig:3}). On average, the photometric contrast is
$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W.

@@

We find that the amplitudes in the two bands are
significantly different. By fitting Gaussians to the MC fit result
distributions, we determin that the  amplitude for F125W is
1.36\% with a standard deviation of 0.23\%, and  the amplitude for F160W is
0.78\% with a standard deviation of 0.22\%. The amplitudes of two
bands are separated by more than 2-$\sigma$. The amplitude
for F125W is $1.74\pm0.30$ times of that for F160W light curve.

@@

% A fundamental result of our study is the direct determination of the
% rotation period of a directly imaged planetary-mass object. We
% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
% brown dwarfs with well defined rotation period from the study of
% \cite{Metchev2015}, and compare their rotation velocities with solar
% system planets and \bpic{} b in the left
% panel of Figure \ref{fig:5}.  The study by
% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
% and demonstrated that it fits a trend defined by Solar System planets
% in which more massive planets have faster rotation rates. They suggested
% that this relation is linked to the accretion processes during planet
% formation.

\reviseTwo{Because the period of modulation is longer than the
  observation time baseline, the most suitable method to constrain
  period is to fit the light curves with physical viable model. The light curve of a planetary mass
  companion is either a complete flat line, or a periodical curve with
  constant mean for which a sine wave is the most simple form. On the contrary,
  2M1207b is not likely to constantly getting bright or faint. The
  flatness of the light curves of 2M1207A demonstrate that there is no
  instrumental sensitivity drift or any similar effect that can
  introduce a $\sim9$ hour slope. We do include very 
  long period sinusoid as possible solution for our MC fit, and
  demonstrate that a sinusoid with period of $\sim10$
  hour is the most probable solution with or without including data
  from the first orbit. In the paper, we include the whole photometric
  data, which can be combined with data available in the future to
  carry out more rigorous period measurement.}

An important result of our study is the direct measurement of the
photometric modulation period of a directly imaged planetary-mass
object.

We infer the rotation period of
2M1207b to be the same as the period of photometric
variation. Although horizontal winds can cause the measured period to
differ from true rotation period, it is unlikely that the difference
is greater than the uncertainty of the measurement, since for Jupiter
and Saturn, typical wind speeds are more than one order of magnitude
smaller than the equatorial rotation speeds.
% Our
% inferred rotation period of 2M1207b is typical among those of brown dwarfs
% \citep{Reiners2008}.
In the left panel of Figure~\ref{fig:5} we compare the rotation period
of 2M1207b to the solar system planets, \bpic{} b the only other
directly imaged planet with an estimated period and measured \vsini,
field brown dwarfs from the study of \citet[][]{Metchev2015},
\revise{and young brown dwarfs (UpSco, age $\sim 11$ Myr) from
  \citet[][]{Scholz2015}}. \citet[][]{Snellen2014} measured \vsini{}
for \bpic{} b and demonstrated that it fits a trend defined by Solar
System planets in which more massive planets have faster rotation
rates. The interesting finding that \bpic{} b, an exoplanet that
formed in a protoplanetary disk, follows this trend suggests a
possibly connection between planet mass, initial angular momentum, and
formation in a disk.

@@

\revise{ The rotation period of $\sim 10$
  hour is significantly longer than those of field brown dwarfs from the sample
  of \cite{Metchev2015}, and the corresponding equatorial rotation
  speed ($\sim 15\, \mathrm{km\,s^{-1}}$) is lower than most L-type field
  brown dwarfs \citep[][]{Reiners2008}.
  In contrast, the rotation period of 2M1207b is similar to the median period
  of the sample of \cite{Scholz2015}, whose age is similar
  to 2M1207b. The rotation period of 2M1207b
  is agreed within the range predicted by evolutionary track
  established from measurements of brown dwarfs assuming conservation
  of angular momentum \citep[see Fig. 4 of ][]{Scholz2015}, and much longer
  than the break-up limit \citep{Marley2011}, i.e. the rotation period where the
  equatorial centrifugal force exceeds gravitational force. Observed
  rotation rates for brown dwarfs of different ages show little
  evidence for angular momentum loss at the age of several Myr in contrast to low-mass stars
  \citep{Bouvier2014, Scholz2015}, and agree with the model of solid
  body rotation for the fully convective interior. Rotation periods of
planetary mass objects with well established age measurements can
place stronger constrain on their internal structures.}

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\bibliographystyle{apj}

\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref}
\shortauthors{Zhou et al.}

%%% new command %%%
\newcommand{\ima}{\texttt{ima} files }
\newcommand{\flt}{\texttt{flt} files }
\newcommand{\eps}{$\mathrm{e}^{-}/\mathrm{s}$}
\newcommand{\tinytim}{\textit{Tiny Tim}}
\newcommand{\bpic}{$\beta$ Pic}
\newcommand{\vsini}{$v\sin i$}
\newcommand{\mjup}{M$_{\mbox{Jup}}$}
\newcommand{\revise}[1]{\textbf{{\color{cyan}{#1}}}}
\renewcommand{\revise}{}
\newcommand{\reviseTwo}[1]{\textbf{{\color{cyan}{#1}}}}
\newcommand{\period}{$10.7^{+1.2}_{-0.6}$}
\newcommand{\Jperiod}{$11.1^{+2.0}_{{-1.2}}$}
\newcommand{\Jperiodd}{$11.9^{+3.4}_{-1.8}$}
\newcommand{\Jamp}{$1.36\pm0.23 \%$}
\newcommand{\Hperiod}{$9.3^{+2.0}_{{-0.8}}$}
\newcommand{\Hperiodd}{$10.7^{+4.4}_{{-1.4}}$}
\newcommand{\Hamp}{$0.78\pm0.22 \%$}
\begin{document}

@@

\begin{abstract}
  Rotational modulations of brown dwarfs have recently provided
  powerful constraints on the properties of ultra-cool atmospheres,
  including longitudinal and vertical cloud structures and cloud
  evolution. Furthermore, periodic light curves directly probe the
  rotational periods of ultra-cool objects.  We present here, for the
  first time, time-resolved high-precision photometric measurements of
  a planetary-mass companion, 2M1207b.  We observed the binary
  system with HST/WFC3 in two bands and with two spacecraft roll
  angles. Using point spread function-based photometry, we reach a
  nearly photon-noise limited accuracy for both the primary and the
  secondary. While the primary is consistent with a flat light curve,
  the secondary shows modulations that are clearly detected in the
  combined light curve as well as in different subsets of the data.
  The amplitudes are 1.36\% in the F125W and 0.78\% in the F160W
  filters, respectively.  \reviseTwo{By fitting sine waves to the
  light curves,} we find a consistent period of
\period{} hours and
  similar phases in both bands. The J- and H-band amplitude ratio of
  2M1207b is very similar to a field brown dwarf that has identical
  spectral type but different J-H color.  Importantly, our study also
  measures, for the first time, the rotation period for a directly 
  imaged \reviseTwo{extra-solar planetary-mass companion.}
\end{abstract}

@@

The observations applied space craft rolls each two orbits to allow
roll-subtraction of the primary \citep[e.g.][]{Song2006}. The
telescope roll angles for orbit 1, 3, and 5, and those for 2, 4, and 6
differed by $25^{\circ}$. At the separation of 2M1207b, this angle
difference corresponds to a displacement of $0.34''$, or 2.75 and 2.30
resolution elements in F125W and F160W, respectively.
%In each orbit we took 8 SPARS10 exposure sequence with NSAMP=10,
%alternating between F160W and F125W filters, with 2--3 identical
%exposures in each exposure sequence.

\reviseTwo{In each orbit, we used the visibility of 2380s, which allowed us
  to take eight SPARS10 exposure sequences
  alternating between the F125W and F160W filter. Each sequence contained
  2--3 identical exposures of 88.4 s with 10 non-destructive read-outs. The number of exposures were limited by
  time spent on filter switching and transferring the data from the
  instrument to the data processing computer.} To improve sampling and reduce the risk
that the core of point spread function (PSF) is affected by bad
pixels, we applied a 4-point dither pattern with differential ``X/Y''
offsets of 1.375" in the detector frame, providing optimal
non-integral (half pixel) step of 10.5 and 8.5 pixels in F125W and
F160W, respectively. In total, we obtained 70 and 64 images  in
F125W and F160W, respectively.

@@

 \begin{figure*}
  \centering
  \plotone{systematics}
  \caption{F125W (left) and F160W (right) light curves under different
    variability verification tests. Individual measurements are
    plotted with gray crosses. Photometric measurements of the same
    exposure sequence are binned, and binned photometry are plotted
    with points or squares. Best fitted sinusoids are plotted with
    solid lines. {\em Upper}: binned measurements taken in dithering
    position 1 and 3 (red points) and that taken in 2 and 4 (blue
    squares) are plotted with different symbols. \reviseTwo{The two halves
      of data were reduced independently, and show the same modulation
      trend.} In upper left panel, the green line a sinusoid fitted
    with all parameters freely varying, and the purple line is a
    sinusoid fitted with the period set the same as that of
    F125W. {\em Middle}: sinusoids fitted without using the data taken
    in Orbit \#1. These curves are almost identical to the curves
    plotted in upper panel. {\em Lower}: photometry measured with
    AFEM-added images and best fitted sinul curves. These points and
    curves are also almost identical to those plotted in the upper
    panel. \reviseTwo{The slight difference of normalized photometry
      among panels for the same filters is the result that
      normalization factors change when omitting the first orbit or when
      adding artificial noise.}}
  \label{fig:2}

@@

For both of 2 steps, we used \tinytim{} to calculate 10$\times$
over-sampled model PSFs based on the filters, the spectra (2M1207A:
\cite{Bonnefoy2014}, 2M1207b: \cite{Patience2010}), the telescope's
actual focus, and the telescope jitter.  We used the set of \tinytim{}
parameters provided by \cite{Biretta2014} to improve modeling the cold
mask, diffraction spikes, and the coma. The focus parameters are 
interpolated to the precise time of the observations using the
tabulated values provided by
STScI\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}.
To align the \tinytim{} PSF to the observed PSF of 2M1207A, we
moved the over-sampled PSF on a coordinate grid (gird size=0.001 pixel)
using cubic interpolation, and searched for the position that minimizes
the rms difference of the observed and the re-binned \tinytim{} PSF over
a region centered on 2M1207A with a 5-pixel-radius aperture centered
on 2M1207b excluded.  Then we introduced another \tinytim{} PSF for
2M1207b and fit the position of 2M1207b and the scales of the
\tinytim{} PSFs of 2M1207A and b simultaneously by minimizing the
residual from both primary and secondary. In the first step, we discovered that the
difference of observed PSFs and model PSFs was very stable for a
specified telescope roll angle and dithering position. Therefore, at the end of the first step,
we derive 8 (2 roll angles $\times$ 4 dithering positions) correction
maps for each filter:
\begin{equation}
  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
\end{equation}
where $\mathrm{PSF_{model}}$ was a combination of two scaled \tinytim{} PSFs
for 2M1207A and b. In the second round, we combined the correction
map linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
and scaled the correction map together with the two PSFs so that the
residual, which is expressed as
\begin{equation}
  \mathrm{Residual} = \mathrm{Image} - a\times \mathrm{PSF_{A}} - b\times
    \mathrm{PSF_{b}}- c\times\mathrm{ Corr}
  \end{equation}
  is minimized by least square fitting.
We found that by introducing the correction term,
the reduced $\chi^{2}$ decreased from $\sim 10$ to
$\sim 1$. Relative photometry was acquired from the scaling
parameters of the \tinytim{} PSFs.

Our final step was to correct for a slight apparent trend between the
position of the targets on the detector and their fluxes. We attributed
this to a combination of slight changes in the PSF profile due to
pixelation and to the effect of imperfectly corrected pixel-to-pixel
sensitivity variations. We corrected for the apparent
position-dependent flux changes by normalizing each photometric point
by the median of all fluxes measured when the target was at the
same position, i.e. combining data over 6 orbits.  We note that this
correction was small and, as we demonstrate in the next sections,
could not introduce artificial modulations that resemble the long-period
variations that we identified in 2M1207b.

@@

@@

First, we fitted sinusoids independently to the light curves of two
filters to verify the similarity of the signal in the two bands
(Figure \ref{fig:2}, top panel) \reviseTwo{using an Markov Chain Monte Carlo (MCMC)
 approach (for detail see \S\ref{sec:MCMC})}. Inconsistent periods or light curve
shapes would argue against a genuine signal. \reviseTwo{We used
  sinusoids as examples of the simplest periodic functions.} We found that the periods
of the best fit sinusoids were similar, \Jperiod{} h for
F125W and \Hperiod{} h for F160W. These periods are consistent
within the uncertainty. Furthermore, these periods are not close to
any timescales over which HST or WFC3 changes, and are
very different from all timescales present in our observations
(dithering timescales, integration times, and orbital
timescales). \reviseTwo{We note that the period is close to
  the total time span of the observation, however, the probability that
  the period  is equal to or less than the observation time baseline is
  negligible (see \S\ref{sec:MCMC}).}

As a second test, we repeated the analysis neglecting the first
orbit. The motivation behind this test is that, due to spacecraft
thermal settling, the first orbits of HST observations are often
slightly unstable, and are neglected in high-precision studies
\citep[e.g.][]{Mandell2013}. Indeed, in our analysis, 2M1207A is
significantly fainter in the first orbit (Figure \ref{fig:3}) than in
the subsequent ones.  \reviseTwo{Our analysis based on orbits 2--6 found the
periods were \Jperiodd{} hours for F125W and \Hperiodd{} hours for F160W, }
which were almost identical results to our analysis using the whole 6 orbits, based on
which we conclude that the first less reliable orbit does not affect
our results significantly (Figure \ref{fig:2}, middle panel).

@@

\subsection{Amplitude and Period Measurements}
\label{sec:MCMC}
% We used a MC method to analyze the light curve, and provided amplitudes
% and periods as well as their uncertainties for both filters. We
% generated series of Gaussian distributed random noise with standard deviation
% same as the photon noise, added the noise to the original light curves, and
% fitted sinusoids to the newly combined light curves. We repeated these
% procedures  for 100,000 times and obtain the distributions of period
% and amplitude (Figure \ref{fig:4}).

@@

\revise{To constrain the amplitudes and periods of the light curves,
  we performed sinusoidal fit using MCMC method.  The priors for the
  amplitudes, the periods and the phases of the sine waves were all
  assumed to be uniform distributions. The ranges of the prior
  distributions were 0 to 5\% for the amplitudes, 2 to 40 hours for
  the periods, and 0 to $2\pi$
  for the phases. The results of the MCMC fit are shown in Figure
  \ref{fig:4}. The posterior distributions of the periods and
  amplitudes are very well constrained for both two filters so that we
  are able to measure the amplitudes and periods as well as their
  uncertainties. For F125W, the amplitude and period are \Jamp{} and
  \Jperiod{} \reviseTwo{hours}, respectively, and for F160W, they are
  \Hamp{} and \Hperiod{} \reviseTwo{hours},
  respectively. \reviseTwo{Next, to place the strongest constraint on
    the period of 2M1207b, we jointly fitted the two light curves
    requiring an identical period for two filters but allowing
    different phases and amplitudes. The period measured from the
    posterior distribution of the joint fit is \period{} hours.} We
  also repeated the fitting excluding data from the first orbit in
  order to quantitatively assess the influence of these less stable
  data points. Even in the case of limiting our data to Orbits 2-6,
  the posterior probability distribution peaks at periods and
  amplitudes very similar to those found for the entire dataset,
  demonstrating that a periodic solution is preferred with or without
  the first orbit data. Nevertheless, unsurprisingly, when shortening
  the baseline by considering only Orbits 2-6 results in a long-period
  tail in the probability distribution.}

\reviseTwo{To evaluate the possibility of very long period sinusoids,
  we integrated the posterior distributions for periods at least
  2$\sigma$
  longer than the best fit period, as well as for periods longer than
  20 hours. For the joint fit, the integrated probabilities are
  12.68\% longer than and 1.29\% for the period longer than 13.1
  ($\mathrm{best\, fit + 2}\sigma$)
  hours and 20 hours, respectively. Given these results we conclude
  that periods much longer than our baseline are very unlikely.}

@@

\section{Result}
\label{Results}

We present the first high-contrast, high-cadence, and high-precision
photometry of a directly imaged planet or planetary-mass
companion around another star. Our observations reveal a modulation in the light curve of
the $\sim 4 \mathrm{M_{{Jup}}}$ companion 2M1207b, the first detection
of modulations in directly imaged planetary-mass objects. The best
fit periods for F125W and F160W are $11.1_{-1.2}^{+2.0}$  and $9.3_{-0.8}^{+2.0}$ hours,
respectively. Jointly fitting the two light curves gives a period
measurement of \period{} hours.

We obtained high signal to noise photometry for both 2M1207A
and B (Figure \ref{fig:3}). On average, the photometric contrast is
$6.52\pm0.01$ mag for F125W and $5.77\pm0.01$ mag for F160W. We
provide our photometry result data in Table \ref{tab:F125W}, \ref{tab:F160W}.

@@

We find that the amplitudes in the two bands are
significantly different. By fitting Gaussians to the MCMC fit result
distributions, we determin that the  amplitude for F125W is
1.36\% with a standard deviation of 0.23\%, and  the amplitude for F160W is
0.78\% with a standard deviation of 0.22\%. The amplitudes of two
bands are separated by more than 2-$\sigma$. The amplitude
for F125W is $1.74\pm0.30$ times of that for F160W light curve.

@@

% A fundamental result of our study is the direct determination of the
% rotation period of a directly imaged planetary-mass object. We
% convert the rotation period to equatorial velocity  by adopting a radius of 1 -- 1.4
% $R_{\mathrm{Jup}}$ for 2M1207b, and 1 $R_{\mathrm{Jup}}$ for field
% brown dwarfs with well defined rotation period from the study of
% \cite{Metchev2015}, and compare their rotation velocities with solar
% system planets and \bpic{} b in the left
% panel of Figure \ref{fig:5}.  The study byf
% \citep[][]{Snellen2014} succeeded in measuring \vsini{} for \bpic{} b
% and demonstrated that it fits a trend defined by Solar System planets
% in which more massive planets have faster rotation rates. They suggested
% that this relation is linked to the accretion processes during planet
% formation.
\reviseTwo{The baseline of our observations is not long enough to
  cover a complete period of 2M1207b. This should come as no surprise,
  given the 10-20 hour long periods observed in the Solar System giant
  planets. Nevertheless, as the observations may cover a large
  fraction of the complete rotation of 2M1207b, we can derive the
  probability distribution of the rotation period and the amplitudes
  (in two bands) based on our data. To do this, we assumed an example
  of a simplest periodic functions, a sine wave. Approximating
  periodic or quasi-periodic modulations in light curves with moderate
  signal-to-noise with sine waves is a common approach \citep[e.g.][]{Buenzli2012}.  We
  used this approximation and combine it with an MCMC approach in
  \S\ref{sec:MCMC} to derive posterior probability distributions.}

\reviseTwo{Before discussing our MCMC results for completeness we
  discuss why other, non-periodic functions cannot be considered
  adequate fits to our data. We can exclude a flat (zero slope)
  lightcurve due to its poor fit (reduced $\chi^{2}$=117.3/69,
  76.9/63 for F125W and F160W, respectively). A constant, but non-zero
  slope line provides an improved reduced $\chi^{2}$,
  but is not a physically viable model: 2M1207b's time-averaged
  brightness cannot rapidly increase or decline. A linear decline or
  brightening that is not intrinsic but instrumental in nature can be
  excluded for three reasons: 1) the simultaneously observed 2M1207A
  shows no such modulation; 2) the signal is consistent between
  different filters and different
  parts of the dataset; 3) all known HST thermal responses occur on
  timescales of 1 orbit or shorter \citep{Lallo2005}, inconsistent
  with the modulations in our data. Given that the linear models are
  inconsistent with our data or not physically viable, and the sine
  waves used in our MCMC fits provide lower reduced $\chi^{2}$ than any of
  the linear models in both filters, we adopt those as the simplest
  description of the modulations.  We include sine waves of period as
  long as 40 hours as possible solutions for our MCMC fit to consider
  the possibility of very long period variations. We find that a
  sinusoid with a period of $\sim 11$
  hour is the most probable solution with or without including data
  from the first orbit. When jointly fitting F125W and F160W light
  curves with sinusoids with the same period but independent amplitudes and
  phases, the integrated posterior distributions for periods at least 2-$\sigma$
  larger than the best fit period is 12.7\%, and that for period
  longer than 20 hours is only 1.3\%. Therefore, our observations exclude
  the possibility of a very long period (p$>$20 hours) at a high
  confidence level. Nevertheless, the period measurement should be further
  constrained in the future  when light curves with full phase
  coverage are available.}

The direct measurement of the
photometric modulation period of a directly imaged planetary-mass
object is an import result of our study.
% \revise{Although a linear trend can also provide reasonable fit to
%   the light curves when data from the first orbit are excluded, it is
%   not a physical viable model. The light curve of a planetary mass
%   companion is either a complete flat line, or a periodical curve with constant mean. On the contrary,
%   2M1207b is not likely to constantly getting bright or faint. The
%   flatness of the light curves of 2M1207A demonstrate that there is no
%   instrumental sensitivity drift or any similar effect that can
%   introduce a $\sim9$ hour slope. We do include very 
%   long period sinusoid as possible solution for our MC fit, and
%   demonstrate that a sinusoid with period of $\sim10$
%   hour is the most probable solution with or without including data
%   from the first orbit.}
We infer the rotation period of
2M1207b to be the same as the period of photometric
variation. Although horizontal winds can cause the measured period to
differ from true rotation period, it is unlikely that the difference
is greater than the uncertainty of the measurement, since for Jupiter
and Saturn, typical wind speeds are more than one order of magnitude
smaller than the equatorial rotation speeds.
% Our
% inferred rotation period of 2M1207b is typical among those of brown dwarfs
% \citep{Reiners2008}.
In the left panel of Figure~\ref{fig:5} we compare the rotation period
of 2M1207b to the solar system planets, \bpic{} b the only other
directly imaged planet with an estimated period and measured \vsini,
field brown dwarfs from the study of \citet[][]{Metchev2015},
\revise{and young brown dwarfs (UpSco, age $\sim 11$ Myr) from
  \citet[][]{Scholz2015}}. \citet[][]{Snellen2014} measured \vsini{}
for \bpic{} b and demonstrated that it fits a trend defined by Solar
System planets in which more massive planets have faster rotation
rates. The interesting finding that \bpic{} b, an exoplanet that
formed in a protoplanetary disk, follows this trend suggests a
possibly connection between planet mass, initial angular momentum, and
formation in a disk.

@@

\revise{ The rotation period of $\sim 10$
  hour is significantly longer than those of field brown dwarfs from the sample
  of \cite{Metchev2015}, and the corresponding equatorial rotation
  speed ($\sim 15\, \mathrm{km\,s^{-1}}$) is lower than most L-type field
  brown dwarfs \citep[][]{Reiners2008}.
  In contrast, the rotation period of 2M1207b is similar to the median period
  of the sample of \cite{Scholz2015}, whose age is similar
  to 2M1207b. The rotation period of 2M1207b
  is within the range predicted by evolutionary track
  established from measurements of brown dwarfs assuming conservation
  of angular momentum \citep[see Fig. 4 of ][]{Scholz2015}, and much longer
  than the break-up limit \citep{Marley2011}, i.e. the rotation period where the
  equatorial centrifugal force exceeds gravitational force. \reviseTwo{Observed
  rotation rates for brown dwarfs of show little
  evidence for angular momentum loss 
  \citep{Bouvier2014, Scholz2015} for the first few Myr of evolution, and agree with the model of solid
  body rotation. In contrast, young low
  mass star experience strong angular momentum loss and internal
  angular momentum redistribution at similar ages.} Rotation periods of
planetary mass objects with well established age measurements can
\reviseTwo{place  further constraint on the gravitational contraction and
  angular momentum evolution in the planetary mass regime.}}
